Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-04-02 doc/supplementary_information.Rmd
some images into SI file
updated SI
add corr plot to supplement
updated SI file

---
title: "Supplementary Information: Vulnerability of tree growth"
author: 
date: 
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 2  
bibliography: growth-precip-thailand.bib
suppress-bibliography: false
csl: new-phytologist.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---

@@

@@

@@

@@

>>>>

---
title: "Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments"
author: 
date: 
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 2  
bibliography: growth-precip-thailand.bib
suppress-bibliography: false
csl: new-phytologist.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---

@@

**Authors**  
```{r eval = TRUE, echo=FALSE, warning=FALSE}
# library(flextable)
# set_flextable_defaults(font.family = "Arial", font.size = 9)
team <- read.csv("display/authors.csv", stringsAsFactors = FALSE, check.names = FALSE)

# team <- read.csv("doc/display/authors.csv", stringsAsFactors = FALSE, check.names = FALSE)

# ft <- flextable(team)
# ft <- line_spacing(ft, space = 1, part = "all")
# ft <- autofit(ft)
# ft <- width(ft, 1, width = 1.75)
# ft <- width(ft, 2, width = 1.75)
# ft <- width(ft, 3, width = 3)
# ft
```

Krishna Anujan^1,2^*  ORCiD: `r team$ORCID[1]`  
Sean McMahon^2,3^  ORCiD: `r team$ORCID[2]`  
Sarayudh Bunyavejchewin^4^  ORCiD: `r team$ORCID[3]`  
Stuart J. Davies^3^  ORCiD: `r team$ORCID[4]`  
Helene C. Muller-Landau^3^  ORCiD : `r team$ORCID[5]`  
Nantachai Pongpattananurak^5^  ORCiD: `r team$ORCID[6]`  
Kristina Anderson-Teixeira^1,3^  ORCiD: `r team$ORCID[7]`

@@

<!-- ![](display/env_vars_SI.png) -->

@@

![](display/Fig_SI_species_sensitivities.png)

![](display/Fig_SI_sensitivity_cor_dec.png)

![](display/Fig_trait_intercept_plot.png)

## Individual correlations

![](display/sens_corr.png)

## Variables and their distributions

![](display/explore/twi.png)

![](display/explore/dbh_cii.png)

@@

## Additional models
